Poseidon Adventure

### 2019-05-24 docs/index.Rmd
testing calc_Z in progress

Work TBD applying `calc_stage2age` and `calc_Z` to get true ages

@@

>>>>

@@

<a href="https://sgaichas.github.io/poseidon-dev/TestCalcZ.html" target="_blank">Test Z calc and compare with true annage NOBA - May 24, 2019</a>

May 24: Either `calc_Z` or `calc_stage2age` or both are incorrect if we expect them to exactly match atlantis annual age ouput where it is available. We match in timestep 0, then diverge.
